Lamperti Optimization

### 2020-04-04 MATLAB_Files/MATLAB_readMe/MATLAB_readMe.tex
Both optimizations seems to be working well. I still need to find a fixed point for Lamperti

\begin{figure}[ht!]
\centering
\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood.eps}
\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood_refined.eps}
\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood_more_refined.eps}
\caption{We use the code \textbf{plotLogLikelihood.m} to create this plots. We used about 18 thousand transitions, and we can also see the initial guess.}
\end{figure}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Lamperti Log-likelihood evaluation (1/2): CODE}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Lamperti Log-likelihood evaluation (2/2):}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{../Results/likelihood/lamperti/Log-Likelihood.eps}
\caption{We use the code \textbf{plotLogLikelihood.m} to create this plots. We used about 18 thousand transitions.}
\end{figure}

>>>>

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{../Results/likelihood/normal/Log-Likelihood.eps}
%\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood_refined.eps}
%\includegraphics[width=0.32\textwidth]{../Results/likelihood/normal/Log-Likelihood_more_refined.eps}
\caption{We use the code \textbf{plotLogLikelihood.m} to create this plots. We used about 18 thousand transitions, and we can also see the initial guess.}
\end{figure}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Lamperti Log-likelihood evaluation: CODE}

@@

### 2020-04-04 Reports/20200403 - Moments_all/20200403 - Moments_all.tex
Both optimizations seems to be working well. I still need to find a fixed point for Lamperti

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/histograms/others/forecast_transitions.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/histograms/others/error_measurement.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/histograms/others/error_and_forecast.eps}
\end{figure}
From here we can see that the error transitions are approximately in the interval $[-0.3,0.3]$, and the forecast transitions in the interval $[-0.03,0.03]$.\\
Then, we want to ensure that the moments are well approximated in the rectangle $[-0.3,0.3]\times[-0.03,0.03]$ (for $\Delta V\times\Delta p$).

>>>>

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/histograms/others/forecast_transitions.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/histograms/others/error_measurement.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/histograms/others/error_and_forecast.eps}
\end{figure}
From here we can see that the errors are approximately in the interval $[-0.3,0.3]$, and the forecast transitions in the interval $[-0.03,0.03]$.\\
Then, we want to ensure that the moments are well approximated in the rectangle $[-0.3,0.3]\times[-0.03,0.03]$ (for $V\times\Delta p$).

### 2020-04-04 Reports/20200404 - Lamperti Optimization/20200404 - Lamperti Optimization.tex
Both optimizations seems to be working well. I still need to find a fixed point for Lamperti

\title{Error SDE ($Z_t$) moments}
\subtitle{Renzo Miguel Caballero Rosas}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Data histograms:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/histograms/others/forecast_transitions.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/histograms/others/error_measurement.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/histograms/others/error_and_forecast.eps}
\end{figure}
From here we can see that the errors are approximately in the interval $[-0.3,0.3]$, and the forecast transitions in the interval $[-0.03,0.03]$.\\
Then, we want to ensure that the moments are well approximated in the rectangle $[-0.3,0.3]\times[-0.03,0.03]$ (for $V\times\Delta p$).

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated moments for $Z_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_1.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_1.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_1.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_1.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_1.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_1.eps}
\end{figure}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated moments for $Z_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_2.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_2.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_2.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_2.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_2.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_2.eps}
\end{figure}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated moments for $Z_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_3.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_3.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_3.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_3.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_3.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_3.eps}
\end{figure}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated moments for $Z_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_4.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_4.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_4.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_4.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_4.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_4.eps}
\end{figure}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated moments for $Z_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_5.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_5.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_5.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_5.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_5.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_5.eps}
\end{figure}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated moments for $Z_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_6.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_6.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_6.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_6.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_6.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_6.eps}
\end{figure}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated moments for $Z_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_ODE_7.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_MC_7.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/fm_7.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_ODE_7.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_MC_7.eps}\quad
\includegraphics[width=0.3\textwidth]{../../MATLAB_Files/Results/moments/lamperti/errors/sm_7.eps}
\end{figure}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Approximated moments for $Z_t$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/moments/lamperti/7.eps}
\end{figure}

>>>>

\title{Lamperti Optimization}
\subtitle{Renzo Miguel Caballero Rosas}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Description:}

Let $\{\Delta V_i\}_{i=1}^n$ be the set of all error transitions, and $\psi(\theta_0,\alpha,\Delta V)$ the Lamperti transform. Notice that the Lamperti transitions $\{\Delta Z_i\}_{i=1}^n$ depend on $(\theta_0,\alpha)$ because $$\{\Delta Z_i\}_{i=1}^n=\psi(\theta_0,\alpha,\{\Delta V_i\}_{i=1}^n).$$
Then, if we compute $$\min_{(\theta_0,\alpha)}\mathbf{L}(\theta_0,\alpha,\{\Delta Z_i\}_{i=1}^n),$$
we are \alert{NOT} computing a MLE in the classical sense. However, we can try to find ${\color{blue}(\theta_0^*,\alpha^*)}$ such that $${\color{blue}(\theta_0^*,\alpha^*)}=\arg\min_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{blue}\theta_0^*},{\color{blue}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right).$$
In this point, the likelihood has a maximum for the data set corresponding to that point.
